### 2009-04-11 docs/runtime_parameters/runtime_parameters.tex
add in the parameters that the modified script found
more progress

\verb=  anelastic_cutoff =  &   &  3.e6 \\
\verb=  base_cutoff_density =  &   &  3.e6 \\

@@

\verb=  cg_verbose =  &   &  0 \\

@@

\verb=  chk_int =  & number of timesteps between writing a checkpoint file  &  \\
\verb=  co_latitude =  &   &  ZERO \\

@@

\verb=  do_burning =  &   &  .true. \\
\verb=  do_eos_h_above_cutoff =  &   &  .true. \\
\verb=  do_initial_projection =  &   &  \\
\verb=  do_sponge =  &   &  .false. \\

@@

\verb=  enthalpy_pred_type =  &   &  predict\_rhohprime \\

@@

\verb=  fixed_dt =  &   &  -1.0d0 \\

@@

\verb=  hg_dense_stencil =  &   &  .true. \\
\verb=  init_divu_iter =  &   &  4 \\
\verb=  init_iter =  &   &  4 \\
\verb=  init_shrink =  & the multiplicative factor ($\le 1$) to reduce the initial timestep as computed by the various timestep estimators   &  1.0 \\
\verb=  interp_type_radial_bin_to_cart =  &   &  1 \\

@@

\verb=  lUsingNFiles =  &   &  .true. \\
\verb=  max_dt_growth =  &   &  1.1D0 \\
\verb=  max_grid_size =  &   &  64 \\
\verb=  max_levs =  &   &  1 \\
\verb=  max_step =  &   &  \\

@@

\verb=  mg_verbose =  &   &  0 \\

@@

\verb=  min_width =  &   &  16 \\
\verb=  model_file =  &   &  \\
\verb=  n_cellx =  &   &  \\
\verb=  n_celly =  &   &  \\
\verb=  n_cellz =  &   &  \\
\verb=  nOutFiles =  &   &  \\
\verb=  perturb_model =  &   &  .false. \\
\verb=  plot_base =  &   &  \\

@@

\verb=  plot_int =  &   &  \\
\verb=  plot_spec =  &   &  \\
\verb=  plot_trac =  &   &  \\

@@

\verb=  radius =  &   &  0.75d8 \\

@@

\verb=  restart =  &   &  \\

@@

\verb=  the_copy_cache_max =  &   &  \\

@@

\verb=  the_sfc_threshold =  &   &  \\

>>>>

\verb=  anelastic_cutoff =  & Refer to Section \ref{Sec:Anelastic Cutoff}.  &  3.e6 \\
\verb=  base_cutoff_density =  & Refer to Section \ref{Sec:Base Cutoff Density}  &  3.e6 \\

@@

\verb=  cg_verbose =  & Verbosity of bottom solver.  &  0 \\

@@

\verb=  chk_int =  & number of timesteps between writing a checkpoint file  & 0 \\
\verb=  co_latitude =  & latitude, in radians, for problems with rotation where the domain is only a subset
                             of a full star.  &  ZERO \\

@@

\verb=  do_burning =  & turn on (.true.) or off (.false.) burning  &  .true. \\
\verb=  do_eos_h_above_cutoff =  & After the advective enthalpy update, recompute the enthalpy if we are 
                                         below the base cutoff density.   &  .true. \\
\verb=  do_initial_projection =  & Do the initial projection.  & 1 \\
\verb=  do_sponge =  & Use sponging.  &  .false. \\

@@

\verb=  enthalpy_pred_type =  & predict\_rhohprime = 1; predict\_h = 2; predict\_T\_then\_rhohprime = 3;
                                      predict\_T\_then\_h = 4; predict\_hprime = 5; predict\_Tprime\_then\_h = 6;
                                    &  predict\_rhohprime \\

@@

\verb=  fixed_dt =  & Fix the time step.  If -1.0, then use the standard time step.  &  -1.0d0 \\

@@

\verb=  hg_dense_stencil =  & In hgproject, 
                                   In 2D, use a 9 point Laplacian (.true.) or 5-point Laplacian (.false.).
                                   In 3D, use a 27 point Laplacian (.true.) or 7-point Laplacian (.false.). &  .true. \\
\verb=  init_divu_iter =  & Number of initial divu iterations.  &  4 \\
\verb=  init_iter =  & Number of initial pressure iterations.  &  4 \\
\verb=  init_shrink =  & the multiplicative factor ($\le 1$) to reduce the initial timestep as computed by the 
                             various timestep estimators   &  1.0 \\
\verb=  interp_type_radial_bin_to_cart =  & The interpolation for filling a full multifab from a 1D 
                                                     bin-centered array.  1 = piecewise constant; 
                                                     2 = piecewise linear.  &  1 \\

@@

\verb=  lUsingNFiles =  & If .true., use nOutFiles processors to write checkpoint and plotfiles.  
                              Fortran has the unfortunate feature of each processor only being able to write out 
                              1-2GB each without crashing.  &  .true. \\
\verb=  max_dt_growth =  & The maximum scale factor that the time step is allowed to grow by per time step.  
                              &  1.1D0 \\
\verb=  max_grid_size =  & The largest grid size that will be created using make\_new\_grids.  &  64 \\
\verb=  max_levs =  & Total number of levels.  1 = single level.  &  1 \\
\verb=  max_step =  & Maximum number of steps in the simulation.  & 1 \\

@@

\verb=  mg_verbose =  & Verbsoity of the multigrid solver, but not the bottom solver.  &  0 \\

@@

\verb=  min_width =  & The minimum size on a side  for a grid created using make\_new\_grids.  &  16 \\
\verb=  model_file =  &   & ``model.hse'' \\
\verb=  n_cellx =  & Number of cells for the base level in the x-direction  &  \\
\verb=  n_celly =  & Number of cells for the base level in the y-direction  &  \\
\verb=  n_cellz =  & Number of cells for the base level in the z-direction  &  \\
\verb=  nOutFiles =  & If lUsingNFiles = .true., use this many processors to write checkpoint and plotfiles.  
                           Fortran has the unfortunate feature of each processor only being able to write out 
                           1-2GB each without crashing.  & 64 \\
\verb=  perturb_model =  & Turn on a perturbation in the initial data.  Problem specific.  &  .false. \\
\verb=  plot_base =  &   & .false. \\

@@

\verb=  plot_int =  &   & 0 \\
\verb=  plot_spec =  &   & .true. \\
\verb=  plot_trac =  &   & .false. \\

@@

\verb=  radius =  &   &  1.0e6 \\

@@

\verb=  restart =  &   & -1 \\

@@

\verb=  the_copy_cache_max =  &   & 50 \\

@@

\verb=  the_sfc_threshold =  &   & 5 \\
